---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
First we load the data and convert the dates appropriately:

```{r}
data<-read.csv("../activity.csv")
data$date<-as.Date(data$date)
```

## What is mean total number of steps taken per day?
Group data by day and sum, then output a histogram:

```{r}
daily<-tapply(data$steps, data$date, sum)
hist(daily)
```

Calculate the mean and median steps per day:
```{r}
mean(daily, na.rm=T)
median(daily, na.rm=T)
```

## What is the average daily activity pattern?
Calculate and plot average daily activity:
```{r}
averageintervals<-tapply(data$steps, data$interval, mean, na.rm=T)
plot(averageintervals, type="l", xlab="Interval", ylab="Steps")
```

Find the interval with max average steps:

```{r}
which.max(averageintervals)
max(averageintervals)
```

(Interpret that as minute 835 during the day, 104th element in the array I think)

## Imputing missing values

Calculate number of missing values:
```{r}
sum(is.na(data$steps))
```

Let's fill the missing rows with the average number of steps from the dataset as a whole, and then repeat the steps from above.

```{r}
mean(data$steps, na.rm=T)
data2<-data
data2$steps[is.na(data$steps)]<-37.3
daily2<-tapply(data2$steps, data2$date, sum)
hist(daily2)
mean(daily2, na.rm=T)
median(daily2, na.rm=T)
```

## Are there differences in activity patterns between weekdays and weekends?
